---
title: "21bcs022-ex5"
author: "Nagajothi"
date: "2024-03-13"
output:
  word_document: default
  pdf_document: default
---

## R Markdown

**6.Consider a Titanic dataset and compare metric values across #different subgroups of the data. Also assume you have a greater number of groups, which visualization method do you prefer over a column chart.**

```{r}
 library(readr)

 Titanic<-read.csv("E:/jothi/Titanic (1).csv") 

boxplot(Fare ~ Pclass,data=Titanic,main="Boxplot of Titanic Fare by Passenger class",xlab="Passanger class",ylab="Fare")
```

**7.Consider the below given Data-set and plot different charts.**

```{r}
library(ggplot2)
df<-data.frame(
  EMPID=paste0("EMP",1:10),
  Gender=c("M","F","F","M","F","M","M","F","M","M"),
  Age=c(34,40,37,30,44,36,32,26,32,36),
  Sales=c(123,114,135,139,117,121,133,140,133,133),
  BMI=c("Normal","OverWeight","Obesity","UnderWeight",
      "UnderWeight","Normal","Obesity","Normal","Normal","UnderWeight"),
  Income=c(350,450,169,189,183,80,166,120,75,40)
)
```

**#Create Bar Chart:**

```{r}
ggplot(df,aes(x=Gender)) + geom_bar()+ggtitle("Gender Distribution - Bar Chart")
```

**#Create Histogram:**

```{r}
ggplot(df,aes(x=Age)) + geom_histogram()+ggtitle("Age Distribution - Histogram") 
```

**#Create Scatterplot:**

```{r}
ggplot(df,aes(x=Sales,y=BMI)) + geom_point()+ggtitle("Sales vs BMI - ScatterPlot") 
```

**#Create Boxplot:**

```{r}
ggplot(df,aes(x=Gender,y=Income)) + geom_boxplot()+ggtitle("Gender vs Income - BoxPlot")
```

**#8.Consider the above dataset and draw the box plot for the**

**#statistical data based on the minimum, #first quartile, median, third quartile, and maximum**

```{r}
library(ggplot2)
b<-subset(df,select=c(-EMPID,-Gender,-BMI))
b<-boxplot(b,ylim=c(0,40),main="Boxplot for IRIS",xlab="Features",ylab="Frequency")
b
text(x=1,y=80,paste(max(df$Age),"(max)"))
text(x=2,y=180,paste(max(df$Sales),"(max)"))
text(x=3,y=380,paste(max(df$Income),"(max)"))
text(x=1,y=9,paste(min(df$Age),"(min)"))
text(x=2,y=5,paste(min(df$Sales),"(min)"))
text(x=3,y=8,paste(min(df$Income),"(min)"))
text(x=1,y=60,paste(median(df$Age),"(median)"))
text(x=2,y=160,paste(median(df$Sales),"(median)"))
text(x=3,y=360,paste(median(df$Income),"(median)"))
text(x=1,y=100,paste(quantile(df$Age,0.25),"(First Quantile)"))
text(x=2,y=200,paste(quantile(df$Sales,0.25),"(First Quantile)"))
text(x=3,y=400,paste(quantile(df$Income,0.25),"(First Quantile)"))
text(x=1,y=120,paste(quantile(df$Age,0.75),"(Third Quantile)"))
text(x=2,y=220,paste(quantile(df$Sales,0.75),"(Third Quantile)"))
text(x=3,y=340,paste(quantile(df$Income,0.75),"(Third Quantile)"))

```

**9.Make a scatterplot for the features in the Iris dataset.**

```{r}
library(ggplot2)
install.packages("datasets")
library(datasets)
feature<-iris$Petal.Length
ggplot(iris,aes(x=1:nrow(iris),y=feature)) +
  geom_point() +
  xlab("Sample") +
  ylab("Petals Length(cm)") +
  ggtitle("Iris Dataset - Petal Length")

```

**10.Look at an individual feature in Seaborn through a boxplot.**

```{r}
install.packages("ggplot2")
library(ggplot2)
library(datasets)
feature<-iris$Petal.Length
ggplot(iris,aes(y=feature)) +
  geom_boxplot() +
  xlab("Count") +
  ylab("Petals Length(cm)") +
  ggtitle("Iris Dataset - Petal Length")
```

**#Create a synthetic dataset of 100 entries (randomly generated) #with the given fields and store it in a .csv file:**

**#Generate synthetic data**

```{r}
data <- data.frame(
  StudentId = 1:100,
  Dept = sample(c('CSE', 'EEE', 'ECE', 'CIV', 'BME'), 100, replace=TRUE),
  Sem = factor(sample(1:8, 100, replace=TRUE)),
  GPA = round(runif(100, min=2.0, max=10.0),3)
)
# Save data to CSV
write.csv(data, file = "ex4-studata.csv", row.names = FALSE)

#1. Scatterplot with smooth curve for every semester 
#with Sized points for every Department
library(ggplot2)
library("dplyr")

ggplot(data, aes(x = Sem, y = GPA, color = Dept, size = Dept)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(title = "GPA vs Semester with Sized Points for Every Department",
       x = "Semester",
       y = "GPA") 
```

**#2. Draw subsets of scatterplot to plot GPA for each department. Scatterplot for GPA vs Semester with subsets for each department**

```{r}
ggplot(data, aes(x = Sem, y = GPA)) +
  geom_point() +
  facet_wrap(~ Dept) +
  labs(title = "GPA vs Semester for Each Department",
       x = "Semester",
       y = "GPA")

```

**#3. Overlapping stacked bar chart represents department-wise-semester-wise count. \#(Horizontal bar chart)**

```{r}

# Generate department-wise-semester-wise count data
count_data <- data %>%  group_by(Dept, Sem) %>%  summarise(count = n()) %>% arrange(Dept, Sem)

# Create the overlapping stacked bar chart
ggplot(count_data, aes(x = count, y = Sem, fill = Dept)) +
  geom_bar(stat = "identity", position = "identity", color = "black", horiz=TRUE) +
  labs(title = "Department-wise Semester-wise Count",
       x = "Count",
       y = "Semester") 
```

\#**4.Identify the outlier's using boxplot Create a boxplot to identify outliers in GPA**

```{r}
ggplot(data, aes(y = GPA)) +
  geom_boxplot() +
  labs(title = "Boxplot of GPA",
       y = "GPA")
```

**#5. Draw histograms for count of GPA with different bin width & zoom to see any one region**

```{r}
# To Create histograms for GPA with different bin widths
ggplot(data, aes(x = GPA)) +
  geom_histogram(binwidth = 0.5, fill = "lightblue", color = "black") +
  labs(title = "Histogram of GPA with Bin Width = 0.5",
       x = "GPA",
       y = "Count")

#To Zoom in to see any one region
ggplot(data, aes(x = GPA)) +
  geom_histogram(binwidth = 0.5, fill = "lightblue", color = "black") +
  xlim(8, 10) +  
  labs(title = "Zoomed-in Histogram of GPA (8 to 10)",
       x = "GPA",
       y = "Count")
```
