---
title: "Histogram and Boxplot using R"
author: "Nagajothi-21BCS022"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  word_document: default
---

## Histogram and Boxplot using R

```{r}
data(iris)
library(MASS)
install.packages("ggplot2")
library(ggplot2)
```

**1.Extract the maximum information from a Histogram and Boxplot.**

```{r}
b<-subset(iris,select=-c(Species))
b<-boxplot(b,ylim=c(0,10),main="Boxplot for IRIS")
text(x=1,y=8.2,paste(max(iris$Sepal.Length),"(max)"))
text(x=2,y=4.4,paste(max(iris$Sepal.Width),"(max)"))
text(x=3,y=7.2,paste(max(iris$Petal.Length),"(max)"))
text(x=4,y=3,paste(max(iris$Petal.Width),"(max)"))

```

**2.Consider the iris dataset,create a new variable called boxplot_data that excludes the species column.**

```{r}

boxplot_data<-subset(iris,select=-c(Species))
boxplot(boxplot_data)
```

**3.Create histograms and Illustrate the distribution look like #within the petalLength feature of the Iris data set.**

```{r}
hist(iris$Petal.Length,main="Histogram for petal Length",xlab="Petal Length in cm")
```

**4.Create histograms that plot multiple features at once for any dataset.**

```{r}
hist(iris$Petal.Length,col="green",main="Histogram for IRIS",xlab="Features if IRIS")
hist(iris$Petal.Width,col="pink",add=TRUE)
```

**5.Plot every feature from the Iris data set (excluding species, since it is non-numerical) in a histogram.**

```{r}
hist(iris$Petal.Length,col="blue")
hist(iris$Petal.Width,col="yellow",add=TRUE)
hist(iris$Sepal.Length,col="red",add=TRUE)
hist(iris$Sepal.Width,col="orange",add=TRUE)

```
